\subsection{Safety}
Safety of Tesla cars has always been a focal point of the company.
Every car that Tesla has released on the market has reached at least 5 star rating \cite{Safety}.%forse da unire le frasi e da chiarire esplicitamente di quali stelle si parla 
Furthermore, most of them went even beyond that and to be precise Model S \cite{ModelS-Rating} , Model X and Model 3 reached level maximum safety in all test and as a result they were awarded 5.4 stars rating.%ci stanno gli esempi ma messo così sembra troppo una pubblicità. La frase è comunque di non facile comprensione 
By NHTSA standards all Tesla cars set a new record having the lowest probability of injury, outclassing even recent Volvo cars, which historically have been leaders of this sector. When compared with the Volvo S60, Tesla Model S preserved 63.5 percent of driver residual space vs. 7.8 percent for the Volvo using an innovative solution similar to what adopted in the Apollo Lunar Lander.%Citazione necessaria
Such a feat is as impressive as unusual since many competitors release cars that not only score poorly at NHTSA standard test but also suffer from  numerous factory recalls. 
\newline 
By nature EVs are safer and more reliable since they have fewer mechanical parts compared to a traditional ICE car. This implies that there are no points of failure, other than the battery.% Scrivere l'acronimo ICE per intero, bisogna essere espliciti la prima volta
Consequently their maintenance is also easier, more straightforward and cheaper.%Unire questa frase con la precendente rendendo un periodo più omogeneo 
\newline One may argue that battery packs are dangerous and might catch fire when damaged of overheated. Regarding this, Tesla not only implements the latest state of the art cooling and protection.% Not only implements but..? Da chiarire questo punto, sennò frase da riformulare 
Therefore battery packs can be considered safest on the market.%Possono essere considerate le più sicure sul mercato? se sì, è necessaria la citazione
Nonetheless the company decided to teach firefighters how to deal with a burning Tesla \cite{Tesla Training Fire}.% Nonetheless deve essere usato come contrasto, mentre la frase è i  linea con la precendente. Puoi dire "inoltre la compagnia fornisce un servizio di addestramento specifico per i pompieri per fornirgli gli strumenti necessari al fine di gestire nel miglior modo possibile un incendio di una Tesla"
\newline Tesla's concern for customers safety is so deep that they even try to protect them from themselves since the most flawed part of a car is the driver.% La frase non è chiara. 
\newline Tesla's can recognize if the driver is distracted, is falling asleep and act accordingly.% Manca un avverbio introduttivo, inoltre forse è necessario citare spiegando qual' è il meccanismo che permette tale servizio
In addition the Autopilot system,  not only assists the driver but also can identify and react to different kinds of danger. % Da unire alla precendente in modo logico, spiegare meglio il funzionamento citando la fonte.
\newline As a result Tesla is leading both in the physical Safety and danger prevention departments.


% ----------------------------
\subsection{Security}
This topic was not discussed much during the battle, but it is important to highlight that Tesla cars not only are safe but also secure.% Da cambiare un po' la frase. Non è necessario dire che è stato poco discusso
\newline One of the most common misconceptions is that by being more "digital" than conventional cars, teslas are also more vulnerable.
Articles such as \cite{Security:Theft} do not do justice, as the method described is nearly universal and was used for decades to steal credit cards.%Che metodo? Spiegarlo brevemente oltre alla citazione 
To prevent this sort event from happening again, another verification step was introduced.% Che step? e come è stato aggiunto? Da citare la fonte.
\newline In addition, as seen in \cite{Security:Methods} the company has devised guidelines of conduct and rewards anyone that finds a vulnerability.
% ------------------------------------------------------------
\section{Self-Driving} % Sub-section
To speak about self-driving cars, a quick introduction of different levels of automation is necessary.
\begin{itemize}
    \item Level 0: basic warnings and safety features.
    \item Level 1: shared control of the vehicle
    \item Level 2: full control, driver needs to be ready to react at any time
    \item Level 3: full control,  driver needs to be ready to react in some situations
    \item Level 4: full control,  driver not needed
    \item Level 5: no steering wheel needed, robotic taxi
\end{itemize}
Since the humble beginnings Tesla aimed at innovating everything related to cars.% Da unire alla frase successiva, non sono separate
It was no surprise when in September of 2014 The Autopilot, an advanced assisted driving program was released. At that time the public opinion on self-driving was not positive but the interest was very high \cite{Pilot:Opinion}. It was a risky bet but it paid off as nowadays Autopilot, now at 9-th version, is the most trusted self-driving system around \cite{Pilot:Trust}.% Va bene citare l' Autopilot, ma bisogna spiegare in cosa consiste
Such positive public opinion was achieved by constantly and gradually innovating the system and acting accordingly to the feedback received from the customers.
On the other hand, Waymo which is aiming directly at level 5 automation and is considered one of the sector leaders scored very poorly. % Non va bene citare Waymo in questo modo, è fuori luogo e un attacco diretto non utile al report, siamo nella stessa squadra

As stated in \cite{Pilot:Awareness} in 2018 the consumers are more excited towards the self-driving cars \cite{Feedback Users Autopilot} but also more distrustful. 
In addition \cite{Pilot:Awareness} shows that people want more control, and would be really reluctant to own/enter a level 4 autonomous car. This highlights the demand for level 2 systems, that Tesla pioneered. % Si dovrebbe unire alla frase precedente
Making no mistake, Teslas onboard hardware and software can achieve a level 4 performance \cite{Full Self-Driving} but, the autopilot is currently classified as a Level 2 as the technology is stil not perfect and moreover not wanted \cite{Pilot:Awareness} \cite{Pilot:CheatSheet}.
It is important to mention that the company gradually releases more and more free of charge advanced features through over-the-air software updates as they become safe and reliable.
In this way  the company-customer trust was built over the years.

