\section{Guidelines (to be removed)}
This is the template for the battle report assignment. You are free to adapt the report in the way you wish, but this is what we consider to be essential to the report.\\
\vspace{1em}
Some general guidelines: \\
Each Battle report should be well mapped to the scenario, the vertical component  and the socio-economic component, as explained in the paper about the battles methodology and explained in the class.\\
The work for the battle report is carried out by all team members together, regardless of which side they took during the battle.\\
The report can (and should!) make reference to material provided on the website (e.g. Seeker’s Blog, articles sent to the class...) where appropriate as well as concepts explored in the class.\\
The starting grade will be the same for both teams in the group, based only on the quality of the battle report. This is why it is \textbf{mandatory} that you manage free riding. As it was said in the class, managing group dynamics is part of your learning objectives: if someone is compromising your performance, you should address the problem via the customer service and the teaching team!\\
The report is graded on a scale from 0 to 10 points. The team that won the battle is awarded an extra point.\\
Evaluation criteria are listed here:
\begin{itemize}
\item \textbf{Correctness} (i.e.: providing factually verifiable information; link to the class theme for the battle; appropriate referencing)
\item \textbf{Completeness of the information provided} (i.e.: capacity to connect to other relevant class concepts and relevant actual or prospective social/economic facts)
\item \textbf{Exposition} (i.e.: English proficiency, readability, soundness and catchiness of the story line)
\item \textbf{Argumentation} (i.e.: Capacity to express critical thinking, outlining trade-offs and relevant challenges and issues)
\end{itemize}
The length of each battle report should be around 10-15 pages, including pictures, graphs, headers and references (excluding digital material). \\
Please note that the final grade is not negotiable! Should the final grade not be accepted and should you decide to take the written exam, the evaluation of the battle report can be accounted in the following exam sessions, even across academic years, as substituting the 3rd question. \\
One point of kindness which we ask: since we will collate the battle reports in a single “book” where we will use LaTeX to compile everything, do not alter the formatting of this document excessively. Even better, if you’re familiar with the tool, use the LaTeX template provided at the end of this document!  As a suggestion: work on Google Drive, and then have one single person move everything into LaTeX and fix the formatting. If you use LaTeX… Feel free to go wild! \\
Deliver the report as a PDF file (and the LaTeX source, if you went that way) to i-and-\url{e-team@list.disi.unitn.it} by January 14th 2018 23:59 CET.\\