\section{Setting} % Sub-section
The first battle that we have experienced, was underwhelming. Although the teams were prepared, only few attacks were made and the questions from the public saved the lesson. To not suffer the same fate we sat down and devised specific rules to guarantee  a fierce and enjoyable battle.
First, the audience identity was decided. We chose to address the students as \textbf{\textit{potential investors}}, since we wanted to get rid of brand bias which was going to happen otherwise. The next logical step was to identify what makes a good investment.
To our best knowledge, investors are most interested in the level of risk, past performance, future projections and obviously business plan of a company.
For starters it was decided to analyze in depth the
\textbf{\textit{business plan}}, the projected \textbf{\textit{growth}} and \textbf{\textit{vision}} of both companies for the near and far future. 
The discussion on different \textbf{\textit{business plans}} naturally brought up the topic of \textbf{\textit{electric and ICE cars}}.
Also, since the future of ICE cars is uncertain, it was decided to include also the discussion on  \textbf{\textit{environmental sustainability}} of each company.
We have also analyzed the trends and hot topics in the automobile industry and came to the conclusion that it is a must to discuss \textbf{\textit{self-driving}} strategies, their \textbf{\textit{safety}} as well as the overall \textbf{\textit{safety}} of the vehicles.
As our society is always more connected it was decided to research also product \textbf{\textit{security}} that both companies provide.
\newline For fair-play and due to our engineering background it was decided to focus mostly on a more technological approach to the modus operandi of both companies, to exclude to the major extent the \textbf{\textit{CEO's}} and to consider only \textbf{\textit{information older than 2 weeks}}.
\newline From the get-go, Tesla team was facing an uphill battle since the company financial struggles, instability and production problems are common knowledge.
\newline On the other hand FCA had to prove that even though they were late to enter the EV market and are years behind on safety and innovation, are still competitive and with a plan for years to come even without the leadership of late Sergio Marchionne.


